---
title: "computeTimes"
output: html_document
date: "2022-07-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(janitor)
```

## Computation times to run neural networks of different sizes

Neural network inference computation is the act of runing a neural network on an input to create an output.
In our case, the input to the network is an image, and the output is a list of detected objects and where they were found in the image.

We collected data for running neural network inference computations over a variety of variables in order to determine how the variables affected the speed.

Variables of interest: Model: What model and size of model was used gpu: Was computation done on gpu or not (if not then it is on a CPU) network: Were images sent over a network, and if so was it wired or wireless images: number of images in the test time: in seconds to run all the images fps: Frames per second, calculated by dividing images / time.

First, we read in the data and look at it.

```{r cars}
# remove rows where model is NA.
inference <- read_csv(file = "data/neuralnetworkspeed.csv", skip_empty_rows = TRUE) %>%
  filter(!is.na(model)) %>%
  clean_names()



```

## Plot fps (speed) vs. model

We are interested to understand how different variables affect speed.
Let's look at fps vs. model and gpu

```{r pressure, echo=FALSE}

inference %>%
  ggplot(aes(x = model, y = fps, color = gpu)) +
  geom_boxplot() 


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

Let's also look at fps vs. model and network settings

```{r pressure, echo=FALSE}

inference %>%
  ggplot(aes(x = model, y = fps, color = network)) +
  geom_boxplot() 
```

### gpu is faster

It is clear that running the inference on gpu is faster than running on CPU.
But there is still a large variation in some data.
Let's dig into just the gpu data.

```{r justgpu}

theGPUfilter <- "GPU"
theNetworkFilter <- c("none","wireless","wired")
inference %>%
  filter(gpu %in% theGPUfilter,
         network %in% theNetworkFilter) %>%
  ggplot(aes(x = model, y = fps, fill = network)) +
  geom_col(position="dodge") +
  labs(title = theGPUfilter) +
      ylim(0,45)


```
